### 2019-02-14 tex_v2/manuscript.tex
done writing all sections

\begin{document}
	%abstract - approx. 150 words
	\begin{abstract}
		\blindtext
	\end{abstract}

@@

\section*{Introduction} \info{670 words, reduce to 600 or less in revisions, structure of argument/narrative is good}
%word count: 673
	{The exoskeleton of Coleoptera (beetles) is a hierarchically-structured fibrous composite characterized by variously arranged \textalpha-chitin (N-acetylglucosamine) nanofibrils embedded in a heterogeneous protein matrix.
	Although \textalpha-chitin is brittle and strongly anisotropic\unsure{give some numbers here}, beetle cuticle is simultaneously rigid and tough due to its unique laminate microstructure\unsure{give more numbers here}.
	Beetle cuticle is divided into two structurally and mechanically distinct regions, the (outer) exocuticle and (inner) endocuticle.
	The exocuticle is characterized by a transversely-isotropic helicoidal structure that is comparatively rigid (though brittle) and has been the subject of numerous prior studies\unsure{numbers and refs}.
	By contrast, the endocuticle of beetles is comprised of large, aligned bundles (macrofibers) of chitin that are strongly anisotropic\unsure{numbers again}.
	Arranged in unidirectional laminae, the macrofibers improve cuticle toughness by inhibiting crack formation and propagation between successive plies \cite{Kamp2010,Kamp2015,Hepburn1973}.

	In general, impact-prone areas and exaggerated structures, such as horns and legs exhibit cuticle organization that resists deformation and fracture.
	Acorn weevils in the genus \textit{Curculio} Linnaeus, 1758\footnote{Pursuant to the International Code of Zoological Nomenclature, the first mention of any specific epithet will include the full genus and species names as a binomen (two part name) followed by the author and date of publication of the name.
	This is not an in-line reference; it is a part of the name itself and refers to a particular species-concept as indicated in the description of the species by that author.} are typified by an elongate structure of the head, called the rostrum (snout), which instead exhibits unusual distal flexibility.
	The rostrum is a hollow, strongly curved (over 90$\degree$ in some species), cylindrical, exoskeletal extension of the otherwise nearly-spherical head, which bears at its apex the terminal chewing mouthparts.
	Despite being composed of the same material as other rigid body parts, the snout can be repeatedly bent without evident damage.
	This structure is used by the female to feed and to excavate sites for egg-laying (oviposition); the latter process causes significant, apparently elastic, deformation of the rostrum\improvement{as illustrated in figure 1c}.
	By maintaining constant tension on the snout and rotating around the bore-hole, females are able to flex the rostrum into a near-perfectly straight configuration and thereby produce a linear channel into the fruit; a single female may prepare hundreds of such sites during the adult stage.

@@

		To investigate the effect of these cuticle modifications, we estimated uni-axial membrane and transverse flexural Young's moduli of the cuticle in both the rostral apex and head capsule using Classical Laminate Plate Theory (CLPT), as detailed in our methods.
		We previously derived the effective elastic constants of the cuticle regions of \textit{C.~longinasus}, which we used here to construct constitutive equations for the entire cuticle of that species.
		The cuticle was estimated to have membrane and flexural moduli of $E_m~=~4.77\,\text{GPa}$ and $E_f~=~6.04\,\text{GPa}$, respectively, in the head capsule; however, in the rostral apex we found that these values were reduced by approximately 72\% and 60\%, respectively ($E_m~=~1.36\,\text{GPa}, E_f~=~2.44\,\text{GPa}$).

		To assess the individual contributions of layer thickness and stacking angle sequence to cuticle flexibility in the rostral apex, two hybrid cuticle lay-ups were also modeled, each with only one of the modifications.
		A hybrid configuration with the angle stacking sequence of typical cuticle (i.e., in the head capsule) but possessing the layer thicknesses of the rostral apex had effective moduli $E_m~=~3.73\,\text{GPa}, E_f~=~4.31\,\text{GPa}$, representing 22\% and 29\% decreases from unmodified cuticle, respectively.
		Similarly, a hypothetical cuticle with the layer thicknesses of ordinary cuticle but possessing the angle stacking sequence of the rostral apex (i.e., $\pm45\degree$ angle-ply in the endocuticle) exhibited elastic moduli $E_m~=~3.77\,\text{GPa}, E_f~=~5.76\,\text{GPa}$, representing 21\% and 4.7\% decreases from unmodified cuticle, respectively.

@@

	\section{Force-controlled loading to fracture}
	%word count: 608
		To better characterize the mechanical behavior of the rostrum at failure, we performed tensile testing on the snouts of six \textit{Curculio} species, representing a mixture of closely and distantly related taxa.
		Heads of female specimens of each species were rehydrated by immersion in de-ionized water for 24 hours to simulate the condition of the living tissue (but see Klocke and Schmitz 2009).
		Each specimen was subjected to force-controlled, uniaxial loading to fracture at a constant stress rate of $0.05\,\text{N}\cdot\text{s}^{-1}$ (detailed in Methods).
		We then examined the correspondence between composite structure and mechanical behavior of the snout, using phylogenetic linear mixed effects models to account for phylogenetic non-independence in the residual variances of the models.

		In general, the specimens exhibited a non-linear viscoelastic response curve characterized by a sharp increase in stress at higher strains, terminating in apparently brittle fracture after a period of strain hardening.
		We believe that strain hardening prior to fracture is a consequence of stiff longitudinal axis of the macrofibers becoming more closely aligned to the longitudinal axis of the rostrum, thereby resisting tension more directly at higher strains.
		We observed that the maximum force sustained at the site of failure was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle, at that site.
		Consequently, there was a positive correlation between ultimate tensile strength of the specimen and the ratio of endocuticle to exocuticle cross-sectional area at the site of fracture.

		Although CLPT predicts a positive association between the proportion of exocuticle and stiffness of a generalized cuticle, we found no correspondence between the cross-sectional properties of the fracture site and the gross behavior of the entire rostrum.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to the properties of the entire snout.
		Instead, we found that the uniaxial elastic modulus of the snout under low strain (E-low) was inversely correlated with the ultimate strain and toughness of the snout (as was the secant modulus, E-sec)
		These associations were all found to be statistically significant and independent of species membership.

@@

		From these tests, we infer that the gross elastic behavior of the cuticle is consistent across the genus, in agreement with our current understanding of cuticle mechanobiology.
		It is therefore unlikely that differences in sclerotization or chitin composition within the cuticle are responsible for the mechanical behavior of the rostrum in different species; instead, a single mechanism (i.e. the modified composite profile) confers increased flexibility and tensile strength to the rostral apex in the genus \textit{Curculio}.
		he endocuticle demonstrably contributes more to rostral tensile strength than the exocuticle, likely because of its organization into large bundles of aligned, anisotropic fibers.
		Consequently, the altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant.

@@

%author contributions
%MAJ: did tensile tests, SEM, confocal (if applicable), data analysis.
%MAJ, NC: designed research, micro-CT (if applicable)
%MAJ, NMF: field collection of test specimens, procurement of specimen loans, specimen prep.
%MAJ, NC, NMF: All authors contributed to the writing, review, and revision of the manuscript.
	\section*{Author contributions}
		\begin{description}
		\item[Andrew Jansen] Conducted sectioning and staining, microscopy and imaging, tensile and fatigue testing, statistical analysis, and participated in manuscript preparation.
		\item[Jason Williams] Conducted tensile and fatigue testing, participated in manuscript preparation.
		\item[Nikhilesh Chawla] Facilitated microscopy, tensile and fatigue testing, and participated in manuscript preparation.
		\item[Nico Franz] Facilitated specimen acquisition and imaging, participated in manuscript preparation.
		\end{description}

	\section*{Additional information}
		Supplementary information is available in the online version of the paper.
		Reprints and permissions information is available online at www.nature.com/reprints.
		Correspondence and requests for materials should be addressed to Andrew Jansen.

@@

				Prior to testing, each specimen was placed in de-ionized water for 24 hours to allow full saturation of the cuticle, simulating the condition of live tissue (see also REF).
				Once removed for testing, the specimen was gripped using the cyanoacrylate handles at the marked locations immediately beyond the anterior margin of the rostrum and the posterior margin of the head capsule
				The exposed section of the snout was coated in petroleum jelly using a cotton swab to prevent loss of moisture and stiffening of the specimen during the test.
				Specimens were loaded in a Tryton 250 Microforce Testing System equipped with a 5N load cell and mechanical clamp grip.
				All specimens were subjected to force-controlled uniaxial tension at a rate of $1.0\,\text{gf}\cdot\text{s}^{-1}$ until failure.
				Results were reported only for specimens that did not fracture due to strain accumulation at the interface between the rostrum and the cyanoacrylate handles.

@@

		\subsection*{Constitutive modeling of the cuticle}
			\paragraph*{General Approach}

			\paragraph*{Cuticle profile of model}
				The cuticle of \textit{C.~longinasus} is 50 microns thick; we use \textit{C.~longinasus} because we have constitutive models for the cuticle regions of this species.
				We assumed equal layer thicknesses in the endocuticle of the basal cuticle, and equal thicknesses of exocuticle and endocuticle.
				In the apical cuticle we assumed the exocuticle and upper 8 layers of the endocuticle were each 5 microns thick, with 4 thinner layers of endocuticle, each 1.25\,{\textmu}m thick.
				The angles of the endocuticle layers for both types of cuticle are as described above.

			\paragraph*{Permutations}
				We additionally calculated models for two hypothetical hybrid cuticles: one model has the layer thicknesses of the apex, but fiber orientations of the base, while the second has the fiber orientations of the apex, but the layer thicknesses of the base.

@@

				Using the lay-ups specified for the cuticle permutations, we calculate the extensional stiffness matrix $[A]$, bending stiffness matrix $[D]$, and bending-extension coupling matrix $B$ for each laminate consisting of $n$ layers at a distance $z$ from the laminate mid-plane.
				The elements of these matrices can be found according to:

@@

				For symmetric laminates, $[B] = 0$, and therefore:

@@

				and, by inverting this equation (let $A^* = A^{-1}$) and substituting based on the assumptions above, we infer:

@@

				Thus, given the assumption that $D_{12} = D_{16} = 0$, Young's modulus for the effective transverse flexural elasticity of the laminate can be found by making Eq.~\ref{eqn::bee} specific to transverse flexure of the x-axis and rearranging the terms:

@@

		\subsection*{Statistical analysis}
			\paragraph*{General approach}
				To explore the relationships between the composite structure and mechanical properties of the cuticle, we fit phylogenetic linear mixed-effects models to the data using maximum likelihood estimation.
				In order to control for phylogenetic non-independence in the data, we included the species of each specimen as a random effect in all models.
				We also allowed for correlation in the error term of the models, as specified by a variance-covariance matrix generated from a Brownian motion model of trait evolution along the phylogeny.
				Response variables and covariates were natural-log transformed, as needed, to ensure model residuals were normally distributed and homoscedastic.
				In all models, we tested whether the inclusion of phylogenetic correlation in the model error produced significantly better model fit, using a likelihood-ratio test and $R^{2}_{\sigma}$-difference test between the fully-specified model and a model lacking the phylogenetic effect.

			\paragraph*{Hypothesis testing}
				The following three hypotheses were tested using PGLMMs fitted using ML estimation:
				\begin{enumerate}
				\item The maximum sustained tensile force is proportional to the cross-sectional area of the endocuticle, and \emph{not} that of the exocuticle.
				\item The ultimate tensile strength of the samples is inversely proportional to the ratio of exocuticle to endocuticle at the location of fracture.
				\item Young's modulus of the samples is proportional to the length of the snout.
				\end{enumerate}

				We fitted a fully-specified model with the cross-sectional area of endocuticle and exocuticle at the site of fracture as fixed effects, including an interaction term, and with maximum tensile force sustained prior to fracture as a response variable.
				This model was then compared to models with only cross-sectional area of either endocuticle or exocuticle as the sole fixed effect in the model.
				We then tested the first hypothesis by using likelihood-ratio tests and $R^{2}_{\beta*}$-difference tests between each of the three models.

				The hypothesis that

			\paragraph*{Model selection and fitting}

			\paragraph*{Estimating phylogenetic signal}

		\subsection*{Code availability}

		\subsection*{Data availability}

>>>>

\begin{document}
	%word count: 156
	\begin{abstract}
		The acorn weevil snout exhibits remarkable flexibility and toughness that are derived from from the microarchitecture of its exoskeleton.
		Here we characterize modifications to the composite profile of the rostral cuticle that simultaneously enhance the flexibility and fracture toughness of the distal portion of the snout.
		Using Classical Laminate Plate Theory (CLPT) we estimate the effect of these modifications on the elastic behavior of the exoskeleton.
		Additionally, changes in the relative layer thicknesses and orientation angles of layers in the exoskeleton are related to the tensile and fatigue behavior of the snout in six species of diverse morphology.
		We demonstrate that increased endocuticle thickness is strongly correlated with increased tensile strength in the snout.
		Consequently, snout stiffness is shown to be inversely correlated with fracture toughness.
		Finally, we identify exocuticle rich invaginations both as a likely site of crack initiation in tensile failure and as a source of morphological constraint on the evolution of the snout.

	\end{abstract}

@@

\section*{Introduction}
%word count: 673
	{The exoskeleton of Coleoptera (beetles) is a hierarchically-structured fibrous composite characterized by variously arranged \textalpha-chitin (N-acetylglucosamine) nanofibrils embedded in a heterogeneous protein matrix.
	Although \textalpha-chitin is brittle and strongly anisotropic\unsure{give some numbers here}, beetle cuticle is simultaneously rigid and tough due to its unique laminate microstructure\unsure{give more numbers here}.
	Beetle cuticle is divided into two structurally and mechanically distinct regions, the (outer) exocuticle and (inner) endocuticle.
	The exocuticle is characterized by a transversely-isotropic helicoidal structure that is comparatively rigid (though brittle) and has been the subject of numerous prior studies\unsure{numbers and refs}.
	By contrast, the endocuticle of beetles is comprised of large, aligned bundles (macrofibers) of chitin that are strongly anisotropic\unsure{numbers again}.
	Arranged in unidirectional laminae, the macrofibers improve cuticle toughness by inhibiting crack formation and propagation between successive plies \cite{Kamp2010,Kamp2015,Hepburn1973}.

	In general, impact-prone areas and exaggerated structures, such as horns and legs exhibit cuticle organization that resists deformation and fracture.
	Acorn weevils in the genus \textit{Curculio} Linnaeus, 1758\footnote{Pursuant to the International Code of Zoological Nomenclature, the first mention of any specific epithet will include the full genus and species names as a binomen (two part name) followed by the author and date of publication of the name.
	This is not an in-line reference; it is a part of the name itself and refers to a particular species-concept as indicated in the description of the species by that author.} are typified by an elongate structure of the head, called the rostrum (snout), which instead exhibits unusual distal flexibility.
	The rostrum is a hollow, strongly curved (over 90$\degree$ in some species), cylindrical, exoskeletal extension of the otherwise nearly-spherical head, which bears at its apex the terminal chewing mouthparts.
	Despite being composed of the same material as other rigid body parts, the snout can be repeatedly bent without evident damage.
	This structure is used by the female to feed and to excavate sites for egg-laying (oviposition); the latter process causes significant, apparently elastic, deformation of the rostrum. \improvement{as illustrated in figure 1c}
	By maintaining constant tension on the snout and rotating around the bore-hole, females are able to flex the rostrum into a near-perfectly straight configuration and thereby produce a linear channel into the fruit; a single female may prepare hundreds of such sites during the adult stage.

@@

		To investigate the effect of these cuticle modifications, we estimated uni-axial membrane and transverse flexural Young's moduli of the cuticle in both the rostral apex and head capsule using Classical Laminate Plate Theory (CLPT), as detailed in our methods.
		We previously derived the effective elastic constants of the cuticle regions of \textit{C.~longinasus}, which we used here to construct constitutive equations for the entire cuticle of that species.
		The cuticle of the head capsule was estimated to have membrane and flexural moduli of $E_m~=~4.77\,\text{GPa}$ and $E_f~=~6.04\,\text{GPa}$, respectively; however, in the rostral apex we found that these values were reduced by approximately 72\% and 60\%, respectively ($E_m~=~1.36\,\text{GPa}, E_f~=~2.44\,\text{GPa}$).

		To assess the individual contributions of layer thickness and stacking angle sequence to cuticle flexibility in the rostral apex, two hypothetical cuticle lay-ups were also modeled, each with only one of the modifications.
		The effective moduli of a configuration with the angle stacking sequence of typical cuticle (i.e., in the head capsule) but possessing the layer thicknesses of the rostral apex were calculated as $E_m~=~3.73\,\text{GPa}, E_f~=~4.31\,\text{GPa}$, representing 22\% and 29\% decreases from unmodified cuticle, respectively.
		Similarly, a hypothetical cuticle with the layer thicknesses of ordinary cuticle but possessing the angle stacking sequence of the rostral apex (i.e., $\pm45\degree$ angle-ply in the endocuticle) had effective elastic moduli of $E_m~=~3.77\,\text{GPa}, E_f~=~5.76\,\text{GPa}$, representing 21\% and 4.7\% decreases from unmodified cuticle, respectively.

@@

	\section{Force-controlled loading to fracture}
	%word count: 608
		To better characterize the mechanical behavior of the rostrum at failure, we performed tensile testing on the snouts of six \textit{Curculio} species, representing a mixture of closely and distantly related taxa.
		Heads of female specimens of each species were rehydrated by immersion in de-ionized water for 24 hours to simulate the condition of the living tissue (but see Klocke and Schmitz 2009).
		Each specimen was subjected to force-controlled, uniaxial loading to fracture at a constant stress rate of $0.05\,\text{N}\cdot\text{s}^{-1}$ (detailed in Methods).
		We then examined the correspondence between composite structure and mechanical behavior of the snout, using phylogenetic linear mixed effects models to account for phylogenetic non-independence in the residual variances of the models.
		These associations reported below are statistically significant and, notably, independent of species membership.

		In general, the specimens exhibited a non-linear viscoelastic response curve characterized by a sharp increase in stress at higher strains, terminating in apparently brittle fracture after a period of strain hardening.
		We believe that strain hardening prior to fracture is a consequence of stiff longitudinal axis of the macrofibers becoming more closely aligned to the longitudinal axis of the rostrum, thereby resisting tension more directly at higher strains.
		We observed that the maximum force sustained at the site of failure was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle, at that site.
		Consequently, there was a negative correlation between ultimate tensile strength of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture.

		Although CLPT predicts a positive association between the proportion of exocuticle and stiffness of a generalized cuticle, we found no correspondence between the cross-sectional properties of the fracture site and the gross behavior of the entire rostrum.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to the properties of the entire snout.
		Instead, we found that the uniaxial elastic modulus of the specimen under low strain (E-low) was inversely correlated with ultimate strain and fracture toughness (as was the secant modulus, E-sec).
		We therefore can infer that stiffer specimens, and by extension, stiffer cuticle profiles, are generally more brittle.

@@

		From these tests, we infer that the gross elastic behavior of the cuticle is consistent across the genus, in agreement with our current understanding of cuticle mechanobiology.
		It is therefore unlikely that differences in sclerotization or chitin composition within the cuticle are responsible for the mechanical behavior of the rostrum in different species; instead, a single mechanism (i.e. the modified composite profile) confers increased flexibility and tensile strength to the rostral apex in the genus \textit{Curculio}.
		In addition, the endocuticle demonstrably contributes more to rostral tensile strength than the exocuticle, likely because of its organization into large bundles of aligned, anisotropic fibers, leading to a trade-off between rigidity and toughness.
		Consequently, the altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant.

@@

%author contributions
%MAJ: did tensile tests, SEM, confocal (if applicable), data analysis.
%MAJ, NC: designed research, micro-CT (if applicable)
%MAJ, NMF: field collection of test specimens, procurement of specimen loans, specimen prep.
%MAJ, NC, NMF: All authors contributed to the writing, review, and revision of the manuscript.
	\section*{Author contributions}
		M.A.J. conducted sectioning and staining, microscopy and imaging, tensile and fatigue testing, statistical analysis, and participated in manuscript preparation.
		J.W. conducted tensile and fatigue testing and participated in manuscript preparation.
		N.C. facilitated microscopy, tensile and fatigue testing, and participated in manuscript preparation.
		N.M.F. facilitated specimen acquisition and imaging and participated in manuscript preparation.

	\section*{Additional information}
		Supplementary information is available in the online version of the paper.
		Reprints and permissions information is available online at www.nature.com/reprints.
		Correspondence and requests for materials should be addressed to M.A.J.

@@

				Prior to testing, each specimen was placed in de-ionized water for 24 hours to allow full saturation of the cuticle, simulating the condition of live tissue (see also REF).
				Once removed for testing, the specimen was gripped using the cyanoacrylate handles at the marked locations immediately beyond the anterior margin of the rostrum and the posterior margin of the head capsule
				The exposed section of the snout was coated in petroleum jelly using a cotton swab to prevent loss of moisture and stiffening of the specimen during the test.
				Specimens were loaded in a Tryton 250 Microforce Testing System equipped with a 5N load cell and mechanical clamp grip.
				All specimens were subjected to force-controlled uniaxial tension at a rate of $1.0\,\text{gf}\cdot\text{s}^{-1}$ until failure.
				Engineering stresses and strains (using undeformed specimen dimensions) were reported only for specimens that did not fracture due to strain accumulation at the interface between the rostrum and the cyanoacrylate handles.

@@

		\subsection*{Constitutive modeling of the cuticle}
			\paragraph*{General Approach}
				The effective uni-axial membrane and transverse flexural elastic moduli of idealized cuticle organizations representing both the rostral apex and head capsule were estimated using Classical Laminate Plate Theory (CLPT).
				The composite profiles of both types of cuticle were idealized using the layer thicknesses and stacking sequences observed in \textit{C.~longinasus}.
				This particular species was chosen because we derived the effective elastic constants of the individual components of the cuticle in previous work.
				In addition, \textit{C.~longinasus} exhibits a profile that is typical and representative for the genus \textit{Curculio}, based on examination of the six species used for tensile testing, as described previously.

				For \textit{C.~longinasus} the total thickness of the cuticle in the head and rostrum is roughly 50\,{\textmu}m, as in most specimens of the other examined species.
				In the head capsule, the exocuticle occupies between 30-50\% of the through-thickness of the laminate, with the remaining thickness nearly evenly divided between 12 layers of endocuticle.
				We use the maximum (50\% of through-thickness, or 25\,{\textmu}m) for the model, since the cuticle appears to deviate from this value only in sulci (grooves), pores, and other scattered features of surface sculpture.
				The macrofiber laminae of the endocuticle were assigned a stacking sequence sequence of $0\degree, 90\degree, 30\degree, -60\degree, 60\degree, -30\degree, 90\degree, 0\degree, -60\degree, 30\degree, -30\degree, 60\degree$, thereby representing pairs of orthogonal plies stacked at a constant rotation angle of $30\degree$, in approximation of the living tissue.

				In the rostral apex, the exocuticle is reduced to a thin shell approximately 5\,{\textmu}m in thickness, or 10\% of the total cuticle thickness.
				The endocuticle displays a more complex pattern of layer thicknesses in the rostral apex than in the head capsule.
				Each of the eight outermost layers are of nearly equal thickness to the exocuticle (5\,{\textmu}m), while the four innermost layers have a combined thickness equal to that of the exocuticle or a single layer of outer endocuticle ($h_{outer}=5\,\text{{\textmu}m}, h_{inner}=1.25\,\text{{\textmu}m}$).
				The stacking sequence with respect to the longitudinal axis of the rostrum forms an antisymmetric [$\pm45\degree$] angle-ply laminate.

				To assess the individual contributions of layer thickness and stacking angle sequence to cuticle flexibility in the rostral apex, two hypothetical cuticle lay-ups were also modeled, each with only one of the modifications present in the cuticle of the rostral apex.
				The first of these models has the layer thicknesses of the rostral apex, but fiber orientations of the head capsule, while the second has the fiber orientations of the rostral apex, but the layer thicknesses of the head capsule.

				Because these laminates are not symmetric, there exists for each a bending-extension coupling matrix $[B]$ populated with non-zero terms, thus complicating the calculation of effective in-plane elastic moduli.
				To circumvent this difficulty and enable meaningful comparison between each laminate, all of the layups are reflected about their inner surface.
				This effectively doubles their thickness while producing a balanced, symmetric laminate with no coupling between bending and extension (i.e., $[B]=0_{3,3}$).
				Estimation of in-plane elastic constants from the extension($[A]$) and bending ($[D]$) matrices is described in detail below; Matlab R2018b was used to numerically evaluate the final values of the effective elastic constants.

@@

				Using the lay-ups specified for each type of cuticle described above, we calculate the extensional stiffness matrix $[A]$, bending stiffness matrix $[D]$, and bending-extension coupling matrix $[B]$ for each laminate consisting of $n$ layers at a distance $z$ from the laminate mid-plane.
				The elements of these matrices can be found according to:

@@

				For symmetric laminates, $[B] = 0_{3,3}$, and therefore:

@@

				and, by inverting this equation (let $A^* = A^{-1}$) and substituting $A^*_{12} = A^*_{16} = 0$ based on the assumptions above, we infer:

@@

				Thus, given the assumption that $D^*_{12} = D^*_{16} = 0$, Young's modulus for the effective transverse flexural elasticity of the laminate can be found by making Eq.~\ref{eqn::bee} specific to transverse flexure of the x-axis and rearranging the terms:

@@

		\subsection*{Statistical analysis}
			\paragraph*{Model selection and fitting}
				In order to explore the relationships between the composite structure and mechanical properties of the cuticle, we fit phylogenetic linear mixed-effects models (PGLMM) to the tensile testing data using maximum likelihood estimation.
				Model exploration and fitting was conducted in \texttt{R version 3.5.1 (2018-07-02) -- ``Feather Spray''} using the \texttt{`nlme'} and \texttt{`ape'} packages.
				Response variables and covariates were natural-log transformed, as needed, to ensure that the normalized model residuals were normally distributed [\texttt{R:shapiro.test}] and homoscedastic [\texttt{R:levene.test}], using numerical and graphical analysis (see Supplementary Data).
				In order to control for phylogenetic non-independence in the data, we included the species of each specimen as a random effect in all models.
				We also allowed for correlation in the error term of the models, as specified by a variance-covariance matrix generated from a Brownian motion [\texttt{R:`ape':corBrownian}] model of trait evolution along a phylogeny.

				The preferred phylogeny for North American \textit{Curculio} is that of (REF-Bonal et al 2016); this phylogeny was generated using Maximum-Likelihood methods and is untrametric, but has uniform internal branch lengths.
				The preferred tree was pruned to include only those species used in tensile testing, with a polytomy at each species to represent the individual specimens examined for that species.
				Because the branch lengths of the tree were not specified, all branch lengths were set equal to 1.
				In general, phylogenetic regression is very robust with respect to missing or incomplete branch length data; underestimation of branch length causes overestimation of phylogenetic signal, which was not found to be statistically significant for any of our models, and we therefore believe that this procedure does not affect the findings of this study.

				Other models of trait evolution were considered during model exploration, including Ornstein-Uhlenbeck [\texttt{R:`ape':corMartins}] and variable rate (AC/DC) [\texttt{R:`ape':corBlomberg}] models.
				However, neither of these produced a significantly better fit to the data than the Brownian motion model for any comparison, as measured by likelihood score and residual variance, viz. $R^2_{\sigma}$, and $R^2_{\beta*}$ [\texttt{R:`r2glmm':r2beta}] (see Supplementary Data).
				$R^{2}_{\sigma}$ is the proportion of generalized variance explained by fixed effects, and is generally used to compare between covariance structures (REF).
				$R^2_{\beta*}$ measures the multivariate association between the outcome and the fixed effects within a given correlation structure, and is generally used to compare between fixed effects (REF).
				We additionally estimated the phylogenetic signal in the residual variance of each model using two measures of spatial autocorrelation (Abouheif's $\bar{C}$ and Moran's $I$) and two measures of phylogenetic signal (Pagel's $\lambda$ and Blomberg's $\kappa$), as detailed below.

				In all models, we tested whether the inclusion of phylogenetic correlation in the model error produced significantly better model fit, using a likelihood-ratio test [\texttt{R:`lmtest':lrtest}] and $R^{2}_{\sigma}$-difference test [\texttt{R:`r2glmm':r2beta(method=`sgv')}] between the fully-specified model and a model lacking the phylogenetic effect.
				Models that incorporated covariance due to Brownian motion consistently produced a higher likelihood score and fit to the data; however, no model exhibited statistically significant phylogenetic signal in any of the variables.
				Once models were fitted to the data, T and F-statistics were calculated to determine whether each cofactor was significantly different from zero.

			\paragraph*{Hypothesis testing}
				Our objectives for hypothesis testing using the PGLMM's were threefold: \textbf{(1)} assess whether the altered ratio of exocuticle to endocuticle in the rostral apex has an effect on the tensile strength of the snout; \textbf{(2)} test whether a trade-off exists between specimen stiffness and resistance to fracture; and \textbf{(3)} examine whether snout length and flexibility are correlated.

				To test the relationship between relative layer thicknesses and tensile strength, we fitted a fully-specified model with the cross-sectional area of exocuticle and endocuticle at the site of fracture as fixed effects, including an interaction term, and with maximum tensile force sustained prior to fracture as a response variable.
				This model was then compared to models with only cross-sectional area of either endocuticle or exocuticle, but not both, as the sole fixed effect in the model.
				We then tested the whether one or both regions was significantly correlated to the maximum force sustained in tension by using likelihood-ratio tests and $R^{2}_{\beta*}$-difference tests between each of the three models.
				We found that only the cross-sectional area of endocuticle was a significant fixed effect, and therefore we elected to remove cross-sectional area of exocuticle as a fixed effect to make the model more parsimonious.
				The final model generated for our first aim featured the ratio of exocuticle to endocuticle in cross-section as a fixed effect, with ultimate tensile strength as the response variable.

				For our second aim we examined the relationship between specimen stiffness and resistance to fracture.
				Specimen stiffness was characterized using a low strain elastic modulus (averaged across the first 33\% of the stress-strain curve) and the secant modulus at failure.
				Resistance to fracture was quantified in terms of failure strain and fracture toughness (measured as area under the stress-strain curve).
				Four models were fitted, two of which had failure strain as the response variable and two with fracture toughness as response variable.
				Each model then used one of the different measures of specimen stiffness as a fixed effect.

				Finally, in the third aim we explored whether a size-effect might exist in the \textit{Curculio} rostrum, particularly if longer (and typically more curved) rostra were more flexible than shorter, straighter rostra.
				We generated two models: the low strain and secant elastic moduli individually served as response variables, with specimen length as the fixed effect in both.

		\subsection*{Code availability}
			R, Python, and Matlab scripts used to manipulate and analyze the raw data (as well as their outputs), produce figures, and estimate effective elastic constants is available from the corresponding author upon request.

		\subsection*{Data availability}
			Stress-strain curves for all tensile and fatigue-tested specimens are provided as PDFs (Supplement 1).
			Diagnostic plots for all PGLMMs are provided as PDFs (Supplement 2). PGLMM terms and output are provided in a PDF (Supplement 3). Raw and processed data will be provided by the corresponding author upon reasonable request.
